%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Android Developer} % Job title
{Synesthesia srl} % Organization
{Full Remote (Turin, Italy)} % Location
{Jan. 2016 - ACTUAL} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Maintained skeleton project of an Android app used for the kick-off of new apps: Clean architecture (Presentation-Data-Domain),   asynchronous tasks execution (RxJava/Coroutines) and dependency injection (Dagger/Hilt).}
		\item {Working with Gradle to build custom plugin for Continuous Integration and utilities.}
		\item {Developed Android applications focusing on architecture and user interface: international sporting events, control of devices for home automation via BLE and using JNI libraries, integration of game and augmented reality modules from Unity3d.}
		\item {5+ years software development using Agile methodologies. }
	\end{cvitems}
}

%------------------------------------------------   

\cventry
{Android and Fullstack Developer} % Job title
{Ennova srl} % Organization
{Turin, Italy} % Location
{Jun. 2013 - Dec. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Leading the design and development of B2C logistics ETL process from SAP to courier data warehouse using cron jobs and LAMP stack.}
		\item {Developed Android applications using Phonegap/Cordova (consumer and business apps).}
		\item {Working with Yii to build CRM modules that is used by back-offices.}
	\end{cvitems}
}

\end{cventries}